\documentclass[12pt]{article}
\usepackage{times}
\usepackage{setspace} % For adjusting line spacing
\usepackage{graphicx}
\usepackage{caption}
\usepackage{float}
\usepackage[numbib]{tocbibind}

\captionsetup[figure]{labelfont=bf, labelsep=period, textfont=bf}

\begin{document}

\title{Developement of Digital Twins of Scientific Equipment and Systems for MegaScience-class Installations.}
\author{
  Denis Zhigalov\\ 
  \small{Master Student.} \\ 
  \small{Department of Computer Technologies,} \\ 
  \small{Novosibirsk State University.} \\
  \small{email: d.zhigalov@g.nsu.ru}
  \and 
  Stanislav Shakirow \\ 
  \small{Scientific Advisor.} \\
  \small{Ph.D. in Physics and Mathematics,} \\
  \small{Associate Professor,} \\
  \small{Department of Computer Technologies,} \\ 
  \small{Novosibirsk State University.} \\
  \small {Acting Director of the Tecnological} \\ 
  \small {Design Institute of Scientific} \\
  \small{Instrument Engineering of the} \\
  \small{Siberian Branch of the RAS.} \\
  \small{email: shakirov@tdisie.nsc.ru}
}
\date{11.10.2023}
\maketitle

\setstretch{1.0} % Set single spacing

\begin{abstract}
    % Your abstract (250-300 words) goes here
\end{abstract}

\textbf{Keywords:} Keyword1, Keyword2, Keyword3, Keyword4, Keyword5

\section{Introduction}
% Introduction section content
In the realm of MegaScience-class installations, the concept of digital twins
has emerged as a transformative technology, offering unprecedented
opportunities for enhancing the design, operation, and maintenance of
scientific equipment and systems. A digital twin is a virtual representation of
a physical asset that enables real-time prediction, optimization, monitoring,
controlling, and improved decision making in scientific equipment and systems
\cite{Rasheed2020Digital}. This technology is not just a theoretical construct
but a practical tool that has been increasingly applied in various fields,
including manufacturing, healthcare, and now, in scientific research
facilities.

The development of digital twins for scientific equipment and systems involves
creating a framework that provides monitoring and evaluation capabilities for
equipment involved in manufacturing and experiments \cite{Duan2021Design}. This
framework is crucial for MegaScience-class installations, where the complexity
and scale of equipment and experiments demand precise and real-time monitoring
for optimal performance and safety.

Moreover, digital twins serve as a new normal form for solving problems in a
changing context, such as in the case of product quality monitoring, as
highlighted by Zhang et al. (2020) in their study on a product quality monitor
model with the digital twin model \cite{Zhang2020A}. This adaptability is particularly
valuable in the dynamic environment of MegaScience installations, where
equipment and systems must consistently operate at peak efficiency under
varying conditions.

The integration of computational models, sensors, learning, real-time analysis,
diagnosis, and prognosis in digital twins supports engineering decisions
related to specific assets \cite{Ritto2021Digital}. This comprehensive approach
is essential for the intricate and high-stakes nature of scientific research,
where even minor miscalculations or malfunctions can lead to significant
setbacks.

In summary, the development of digital twins for scientific equipment and
systems in MegaScience-class installations represents a significant leap
forward in the management and operation of complex scientific infrastructure.
By leveraging the power of virtual modeling, real-time data analysis, and
predictive capabilities, digital twins offer a pathway to more efficient,
reliable, and advanced scientific research.

\section{Literature Review}
% Literature review content

\section{Research Setup}
% Research setup details

\section{Methodology}
% Methodology details

\section{Preliminary Results}
% Preliminary results

% \section{Discussion} % Optional

\section{Conclusion}
% Conclusion

\bibliographystyle{ieeetr}
\bibliography{./biblio}

\end{document}
