\subsection{Utilizing COMSOL Multiphysics for Simulating the Diamond Window in
SKIF}

COMSOL Multiphysics is a versatile and powerful engineering software package
widely used for simulating physical phenomena across various domains. It is
particularly adept at modeling heat and stress fields in materials, making it
an ideal tool for simulating components like the diamond window in the Siberian
Ring Source of Photons (SKIF) \cite{Bachmann2017Numerical, Dudarev2021Study}.
COMSOL provides a comprehensive environment for finite element analysis,
allowing researchers to create detailed models of complex systems and
materials.

In the context of SKIF, COMSOL Multiphysics is employed to simulate the heat
and stress fields of the diamond window and its cooling system. The diamond
window, a critical component in synchrotron radiation sources, must withstand
extreme thermal and mechanical stresses during operation. By using COMSOL, we
can accurately predict how the diamond window will behave under various
conditions, such as different ray positions and cooling water flow rates. This
simulation includes assessing the temperature distribution, thermal stresses,
and potential deformation of the diamond window, ensuring its reliability and
performance in the SKIF facility.% \cite{Codau2022Heat, Boucher2020COMSOL}.

However, one limitation of COMSOL Multiphysics is its inability to run
simulations in real-time. To address this, we use COMSOL to pre-generate heat
and stress data for a set of different parameters. This pre-generated data is
then integrated into the digital twin of the diamond window. The digital twin,
a virtual representation of the diamond window, uses this data to predict the
window's behavior under various operational scenarios. This approach allows for
rapid and accurate assessment of the diamond window's performance without the
need for real-time simulation, making it a practical solution for monitoring
and optimizing the component's operation in SKIF.
% \cite{Gerlich2013COMSOL, Carasi2017SIMULATING}.

In summary, COMSOL Multiphysics plays a crucial role in the development of the
digital twin of the diamond window in SKIF. By providing detailed and accurate
simulations of heat and stress fields, COMSOL enables us to create a robust and
reliable digital twin that enhances the operational efficiency and safety of
the SKIF facility.
